### 2015-10-20 Kokkos_PG_ParallelDispatch.tex
Fixed minor omission of "const"
...  in parallel_reduce functor example.

  // value_type here is already a "reference" type,
  // so we don't pass it in by reference here.
  KOKKOS_INLINE_FUNCTION void
  join (volatile value_type dst,
        volatile value_type src) const {
    for (size_type j = 0; j < value_count; ++j) {
      dst[j] += src[j];
    }
  }

>>>>

  // value_type here is already a "reference" type,
  // so we don't pass it in by reference here.
  KOKKOS_INLINE_FUNCTION void
  join (volatile value_type dst,
        const volatile value_type src) const {
    for (size_type j = 0; j < value_count; ++j) {
      dst[j] += src[j];
    }
  }
